Generating the Blueprints of the Java Ecosystem

### 2015-03-30 msr2015-camera-ready.tex
updated .gitignore; almost there

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{\IEEEauthorblockN{Vassilios Karakoidas\IEEEauthorrefmark{1},
Dimitris Mitropoulos\IEEEauthorrefmark{2},
Georgios Gousios\IEEEauthorrefmark{3},
Diomidis Spinellis\IEEEauthorrefmark{1} and
Panagiotis Louridas\IEEEauthorrefmark{1}}

\IEEEauthorblockA{\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{2}}
\IEEEauthorblockA{\IEEEauthorrefmark{3}}
}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

@@

% no keywords
Java, Software Metrics, Chidamber and Kemerer, Maven

@@

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
\bibliography{msr}

>>>>

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{\IEEEauthorblockN{Vassilios Karakoidas\IEEEauthorrefmark{1},
Dimitris Mitropoulos\IEEEauthorrefmark{2},
Georgios Gousios\IEEEauthorrefmark{3},
Diomidis Spinellis\IEEEauthorrefmark{1} and
Panos Louridas\IEEEauthorrefmark{1}}

\IEEEauthorblockA{\IEEEauthorrefmark{1}Dept of Management Science and Technology\\
Athens University of Economics and Business\\
Athens, Greece\\
\{bkarak,dds,louridas\}@aueb.gr}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Computer Science Department\\
Columbia University\\
New York, United States\\
dimitro@cs.columbia.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Radboud University Nijmegen\\
Nijmegen, the Netherlands\\
g.gousios@cs.ru.nl}}

\maketitle

@@

% no keywords
% Java, Software Metrics, Chidamber and Kemerer, Maven

@@

\bibliographystyle{IEEEtran}
\bibliography{msr}
